Hidden Talents Multiverse Analysis

### 2021-06-28 README.Rmd
trying yet another way

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "data-prep") %>% 
  select(-dir) %>% 
  knitr::kable(format = "pipe")
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "primary-analyses") %>% 
  select(-dir) %>% 
  knitr::kable(format = "pipe")
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "secondary-analyses") %>% 
  select(-dir) %>% 
  knitr::kable(format = "pipe")
```

>>>>

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "data-prep") %>% 
  select(-dir) %>% 
  knitr::kable(format = "simple")
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "primary-analyses") %>% 
  select(-dir) %>% 
  knitr::kable(format = "simple")
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "secondary-analyses") %>% 
  select(-dir) %>% 
  knitr::kable(format = "simple")
```
